Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-09-04 snapshot_system/fast14_evaluation.tex
improve formatting

\subsection{Deduplication Efficiency}
Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC.
Deduplication efficiency is defined as the percent of duplicate chunks
which are detected and deduplicated.
The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
is defined in Table~\ref{tab:symbol}. 
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB
and  the deduplication efficiency can reach over 90\%.
When $\sigma=4\%$, the deduplication efficiency can reach 92\%. 
The loss of efficiency in VC is caused by the restriction of the total physical memory available
in the cluster to support PDS index.  
The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
for global comparison.
In all cases, VC provides similar or better deduplication efficiency than SRB.

@@

%this version combines the old and the minhash alg. to compare against srb
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            width=\linewidth,
            height=0.75\linewidth,
            cycle list={%
                {blue,solid,mark=square*},
                {blue,solid,mark=triangle*,mark size=1.5},
                {blue,solid,mark=diamond*,mark size=1.5},
                %{blue,solid,mark=pentagon*,mark size=1.4},
                {red,draw=red,densely dotted,mark=square},
                %{red,densely dotted,mark=triangle,mark size=1.5},
                %{red,densely dotted,mark=diamond,mark size=1.5},
                {brown,densely dashed,mark=*},
                %{red,densely dotted,mark=o},
                %{red,densely dotted,mark=pentagon,mark size=1.4},
            },
            mark repeat={5},
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            xmin=0,
            ymin=88.5,
            ymax=100,
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            legend columns=2,
            legend style={
                font={\tiny\sffamily},
                %at={(0.5,-0.2)},
                %anchor=north
            },
            ]
            \addplot table[x=VMs,y=MHcds4] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHcds2] {figures/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=MHcds1] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHNocds] {figures/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
            %\addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
            \legend{VC MH( $\sigma=4\%$),
                VC MH($\sigma=2\%$),
                %VC MH($\sigma=1\%$),
                VC MH(No PDS),
                %VC($\sigma=4\%$),
                VC($\sigma=2\%$),
                %VC($\sigma=1\%$),
                SRB
            };
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication efficiency of VC and SRB.}
  \label{fig-exbin-efficiency-graph2}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \epsfig{file=figures/srb_vs_vc, width=3.5in}
  \caption{Time to backup a dirty VM segment under SRB and VC}
  \label{fig:srb_vs_vc}
\end{figure}

>>>>

\subsection{Deduplication Efficiency}
%this version combines the old and the minhash alg. to compare against srb
\begin{figure}[ht]
  \centering
    \begin{tikzpicture}
            \begin{axis}[
            %title={Ex-Binning Efficiency},
            width=\linewidth,
            height=0.75\linewidth,
            cycle list={%
                {blue,solid,mark=square*},
                {blue,solid,mark=triangle*,mark size=1.5},
                {blue,solid,mark=diamond*,mark size=1.5},
                %{blue,solid,mark=pentagon*,mark size=1.4},
                {red,draw=red,densely dotted,mark=square},
                %{red,densely dotted,mark=triangle,mark size=1.5},
                %{red,densely dotted,mark=diamond,mark size=1.5},
                {brown,densely dashed,mark=*},
                %{red,densely dotted,mark=o},
                %{red,densely dotted,mark=pentagon,mark size=1.4},
            },
            mark repeat={5},
            xlabel={Number of VMs added},
            ylabel={Dedup. Efficiency (\%)},
            xmin=0,
            ymin=88.5,
            ymax=100,
            %extra y ticks={4.5,5.5,6.5} %to add extra ticks
            mark options=solid,
            legend pos=south west,
            legend columns=2,
            legend style={
                font={\tiny\sffamily},
                %at={(0.5,-0.2)},
                %anchor=north
            },
            ]
            \addplot table[x=VMs,y=MHcds4] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHcds2] {figures/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=MHcds1] {figures/exbin_efficiency_comparison2.txt};
            \addplot table[x=VMs,y=MHNocds] {figures/exbin_efficiency_comparison2.txt};
            %\addplot table[x=VMs,y=cds4] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=cds2] {figures/exbin_efficiency_comparison.txt};
            %\addplot table[x=VMs,y=cds1] {figures/exbin_efficiency_comparison.txt};
            \addplot table[x=VMs,y=exbin] {figures/exbin_efficiency_comparison2.txt};
            \legend{VC MH( $\sigma=4\%$),
                VC MH($\sigma=2\%$),
                %VC MH($\sigma=1\%$),
                VC MH(No PDS),
                %VC($\sigma=4\%$),
                VC($\sigma=2\%$),
                %VC($\sigma=1\%$),
                SRB
            };
            \end{axis}
    \end{tikzpicture}
    \caption{Deduplication efficiency of VC and SRB.}
  \label{fig:exbin-efficiency-graph2}
\end{figure}

Figure~\ref{fig:exbin-efficiency-graph2} shows the deduplication efficiency for SRB and VC.
Deduplication efficiency is defined as the percent of duplicate chunks
which are detected and deduplicated.
The figure also compares several PDS sizes chosen for VC. ``$\sigma=2\%$'' 
is defined in Table~\ref{tab:symbol}. 
%we allocate the space of distributed shared memory  to accommodate 2\%
%of data chunks shared among VMs, as defined in 
With $\sigma=2\%$, memory usage for PDS index lookup per machine is about 100MB
and  the deduplication efficiency can reach over 90\%.
When $\sigma=4\%$, the deduplication efficiency can reach 92\%. 
The loss of efficiency in VC is caused by the restriction of the total physical memory available
in the cluster to support PDS index.  
The loss of efficiency in SRB is caused by the routing of data chunks which restricts the search scope
for global comparison.
In all cases, VC provides similar or better deduplication efficiency than SRB.

@@

@@

\begin{figure}[htbp]
  \centering
  \epsfig{file=figures/srb_vs_vc, width=3in}
  \caption{Time to backup a dirty VM segment under SRB and VC}
  \label{fig:srb_vs_vc}
\end{figure}
